### 2022-01-11 paper/issta22/experiment.tex
exp

\begin{enumerate}[label=\textbf{RQ\arabic*}:]
\item \label{rq:one} How effective is our proposed evaluation model
  for finding failures given a linguistic capability?
\item \label{rq:two} How effective is our proposed model for
  generating diverse test cases? % self bleu score
\item \label{rq:three} How effective is our proposed model for
  detecting diverse type of errors? % retraining acc score
\item \label{rq:four} How effective is our new test case generation
  using \cfg expansion? % ablation study
\end{enumerate}

@@

For answering \ref{rq:one} and \ref{rq:two}, we organize the experiment as
follows:
%
\MyPara{Selection of seed inputs} \MyPara{\Cfg expansion}
\MyPara{Models}

>>>>

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: How effective is our proposed evaluation model
  for finding failures given a linguistic capability?
\item \label{rq:two}: How effective is our proposed model for
  generating diverse test cases? % self bleu score
\item \label{rq:three}: How effective is our proposed model for
  detecting diverse type of errors? % retraining acc score
\item \label{rq:four}: How effective is our new test case generation
  using \cfg expansion? % ablation study
\end{enumerate}

@@

For answering \ref{rq:one} and \ref{rq:two}, we organize the
experiment as follows: we generate test cases used for model
evaluation.

\MyPara{Seed Input Selection.} For each linguistic capability, we
search all sentences that meet its requirement. Among found sentences,
we randomly select 10 sentences due to space constraint.

\MyPara{\Cfg Expansion.}

\MyPara{Models.}
